%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage{lmodern}
\usepackage{graphicx} % Required for inserting images
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting - Espaciado ligeramente aumentado
\titleformat{\section}{
  \vspace{-2pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-3pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands - Ajustados para más espacio
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-3pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-3pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}
%\setlength{\itemsep}{0pt} % OPTIONAL TO REDUCE LINES

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Angel Perez} \\ \vspace{2pt}
    \small \textbf{Information Systems Engineer - University Systems Analyst}
    --
    \small \textbf{Backend Developer} \\ \vspace{2pt}
    \small \href{tel:+542614699639}{\underline{+54 2614699639}} $|$ \href{mailto:pasaperez@yahoo.com.ar}{\underline{pasaperez@yahoo.com.ar}} $|$ 
    \href{https://www.linkedin.com/in/pasaperez}{\underline{linkedin.com/in/pasaperez}} $|$
    \href{https://github.com/pasaperez}{\underline{github.com/pasaperez}}
\end{center}


\section{Summary}
I am an Information Systems Engineer and Backend Developer with over 7 years of experience designing, modernizing, and maintaining scalable, enterprise-grade web applications. I combine a strong foundation in Full-Stack development, DevOps methodologies, and secure software engineering with proven leadership in establishing coding standards and mentoring high-performing backend and full-stack teams. Specialized in CI/CD processes, production environment management, and delivering robust solutions that significantly improve system availability, drive operational efficiency, and create long-term business value.

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages \& Runtimes}{: Java, JavaScript/TypeScript (NodeJS, V8, Bun), C/C++, Python, R, Dart} \\[3pt]
     \textbf{Backend \& Testing}{: Spring, Hibernate, Express, Sequelize, Mongoose, Jest, JUnit} \\[3pt]
     \textbf{Frontend}{: Angular, React, DurandalJS, Knockout, Thymeleaf, HTML/CSS, AlpineJS, Bootstrap, Flutter} \\[3pt]
     \textbf{Databases}{: MySQL, MariaDB, PostgreSQL, MS SQL Server, SQLite, H2, MongoDB, DynamoDB, Firestore} \\[3pt]
     \textbf{DevOps \& Cloud}{: Git, Docker, Kubernetes, Jenkins, Selenium, GCP, AWS, OpenShift, Groovy} \\[3pt]
     \textbf{Architecture \& Patterns}{: Microservices, Event-driven, REST APIs, MVC, DDD, TDD, BDD, OOP} \\[3pt]
     \textbf{Methodologies}{: Agile (Scrum, Kanban), CI/CD Pipelines, Gitflow, Code Review, Clean Code, DevOps}
    }}
 \end{itemize}

%-----------EXPERIENCE-----------
\section{Professional Experience}

\resumeSubheading
  {Lead Developer}{May 2023 -- Present}
  {Pasaperez Asoc. Simple}{Mendoza, Argentina}
  \resumeItemListStart
    \resumeItem{Led the design and development of two core systems, overseeing architecture, implementation, and deployment processes.}
    \resumeItem{Directed the creation of an exchange integration platform, ensuring efficient data processing and reliable communication between backend services.}
    \resumeItem{Supervised the development of a video analysis and categorization system powered by AI models, driving innovation and automation within the organization.}
    \resumeItem{Ensured code quality, scalability, and adherence to best practices across backend and frontend development teams.}
  \resumeItemListEnd

  \resumeSubheading
  {Backend Technical Expert / Chief Operations Engineer}{Aug 2024 -- Present}
  {Slingr}{US-based company/Remote, Mendoza, Argentina}
  \resumeItemListStart
    \resumeItem{Served as technical reference for the backend team, leading the design and implementation of complex solutions while ensuring technical quality.}
    \resumeItem{Conducted code reviews to ensure deliverables met quality standards, best practices, and established processes.}
    \resumeItem{Managed CI/CD pipelines, supervised cloud infrastructure, and implemented automation processes to optimize deployment workflows.}
    \resumeItem{Proposed and implemented improvements in key areas such as quality, productivity, and internal team processes.}
    \resumeItem{Collaborated in project planning, risk identification, and technical resource allocation.}
  \resumeItemListEnd

  \resumeSubheading
  {Full-Stack Developer}{Nov 2024 -- Present}
  {Slingr}{US-based company/Remote, Mendoza, Argentina}
  \resumeItemListStart
    \resumeItem{Led the development of new full-stack features within the slingr framework and platform, leveraging Angular, React and TypeScript to enhance user experience and backend performance.}
    \resumeItem{Implemented modular front-end components and RESTful APIs, ensuring scalability and maintainability across projects.}
    \resumeItem{Collaborated with cross-functional teams to integrate DevOps practices, automate deployments, and improve CI/CD pipelines.}
    \resumeItem{Contributed to architecture modernization efforts, introducing best practices in code quality, security, documentation, and testing.}
  \resumeItemListEnd

  \resumeSubheading
  {Systems Engineer / Backend Developer}{Dec 2022 -- Oct 2024}
  {Slingr}{US-based company/Remote, Mendoza, Argentina}
  \resumeItemListStart
    \resumeItem{Designed, developed, and maintained key integrations for the slingr platform, ensuring interoperability between services using Java and Node.js.}
    \resumeItem{Delivered internal tech talks on platform architecture and best practices, fostering knowledge sharing across engineering teams.}
    \resumeItem{Worked on core platform components including database management, load balancing, and performance optimization.}
    \resumeItem{Developed and optimized applications within the platform, focusing on new functionalities, APIs, and performance improvements.}
    \resumeItem{Provided comprehensive technical support, ensuring platform availability and stability for 5,000+ users.}
  \resumeItemListEnd
  
  \resumeSubheading
  {Fullstack Software Developer}{Nov 2021 -- Aug 2022}
  {Software del Sur}{Mendoza, Argentina}
  \resumeItemListStart
    \resumeItem{Participated in the development of multiple web platforms including clinical, commercial, and operational management systems.}
    \resumeItem{Developed interfaces for integrations with commercial services using NodeJS (Backend), Angular 8+ (Frontend), and MySQL/MariaDB.}
    \resumeItem{Mentored 5 junior developers, establishing coding standards and conducting code reviews to ensure quality deliverables.}
    \resumeItem{Implemented version control with Git/Bitbucket and managed project requirements with Trello.}
  \resumeItemListEnd

  \resumeSubheading
  {Functional Analyst \& Software Developer}{Mar 2020 -- Aug 2022}
  {Pasaperez Asoc. Simple (Concurrent)}{Mendoza, Argentina}
  \resumeItemListStart
    \resumeItem{Conducted analysis, design, and development of Content Management System for public administration clients.}
    \resumeItem{Utilized Java/Spring/NodeJS (Backend), Angular 14/HTML/JS/CSS/Thymeleaf (Frontend), MS SQL Server, MongoDB (Database).}
    \resumeItem{Deployed solutions using Kubernetes/OpenFaaS on Google Kubernetes Engine (GCP).}
  \resumeItemListEnd

  \resumeSubheading
  {Systems Engineer}{Mar 2021 -- Dec 2021}
  {Grupo Metacod (Concurrent)}{Mendoza, Argentina}
  \resumeItemListStart
    \resumeItem{Led project management, analysis, design, development, testing, and implementation of a Code Generator System with Web Modeler.}
    \resumeItem{Co-authored Metacod System paper presented at 9th National Congress of Computer Engineering (CoNaIISI 2021).}
    \resumeItem{Implemented technology stack: Java/Spring (Backend), ReactJS/HTML/JS/CSS (Frontend), MS SQL Server (Database), Docker (Deployment on Amazon ECS).}
  \resumeItemListEnd

%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Universidad Tecnológica Nacional}{Mendoza, Argentina}
      {Engineering Degree, Information Systems Engineering}{Mar 2014 -- Aug 2022}
    \resumeSubheading
      {Universidad Tecnológica Nacional}{Mendoza, Argentina}
      {Degree, University Systems Analyst}{Mar 2014 -- Aug 2022}
  \resumeSubHeadingListEnd

%-----------PUBLICATIONS & CERTIFICATIONS-----------
\section{Publications \& Certifications}
\resumeSubHeadingListStart
  \resumeSubheading
    {9th National Congress of Computer Engineering (CoNaIISI 2021)}{2021}
    {Co-author of Metacod System research paper}{Argentina}
  \resumeSubheading
    {Introduction to Front-end Development with ReactJS}{2020}
    {Professional Certification}{Online}
  \resumeSubheading
    {Blockchain and Bitcoin Principles}{2020}
    {Professional Certification}{Online}
\resumeSubHeadingListEnd

%-----------LANGUAGES-----------
\section{Languages}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
   \textbf{Spanish}: Native \quad $|$ \quad
   \textbf{English}: Intermediate (B2/C1) \quad $|$ \quad
   \textbf{German}: Basic (A1) \quad $|$ \quad
   \textbf{Italian}: Basic (A1)
  }}
\end{itemize}

%-----------KEY ACHIEVEMENTS-----------
\section{Key Projects \& Achievements}
\resumeSubHeadingListStart
  \resumeProjectHeading
    {\textbf{Slingr Platform Modernization} $|$ \emph{Java, Angular, MongoDB, CI/CD}}{2022 -- Present}
    \resumeItemListStart
      \resumeItem{Led comprehensive platform migration from Java 8 to Java 24, serving 5,000+ active users with enhanced performance and security compliance.}
      \resumeItem{Achieved 30-7000\% performance optimization across multiple core platform processes through architectural improvements and code refactoring.}
      \resumeItem{Orchestrated frontend migration from DurandalJS to Angular and database upgrade from MongoDB 4 to 8, ensuring low-downtime deployment.}
      \resumeItem{Reduced CI/CD build times by 83\% through pipeline optimization and automation improvements.}
      \resumeItem{Successfully achieved HIPAA and SOC 2 security certifications, implementing formal delivery and deployment processes for releases and hotfixes.}
      \resumeItem{Mentored and led a cross-functional team of up to 15 developers, establishing coding standards and best practices.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Metacod Code Generator System} $|$ \emph{Java/Spring, ReactJS, Docker, AWS}}{2021}
    \resumeItemListStart
      \resumeItem{Designed and implemented a web-based code generation system that reduced project initialization time in software factories by 97\% (from 4 months to 1 week) across 4 enterprise projects.}
      \resumeItem{Co-authored and presented research paper at the 9th National Congress of Computer Engineering (CoNaIISI 2021).}
    \resumeItemListEnd

    \resumeProjectHeading
    {\textbf{AI-Powered Video Classification System} $|$ \emph{Bun, AI/ML, Microservices, Benchmarking}}{2025 -- Ongoing}
    \resumeItemListStart
      \resumeItem{Designed and implemented an automated classification system capable of processing up to 8,000 videos and over 500 hours of footage using advanced AI models.}
      \resumeItem{Conducted extensive performance benchmarking to optimize dedicated task execution, achieving significant reductions in computational time and resource utilization.}
      \resumeItem{Engineered the microservices architecture for data processing, ensuring high throughput, scalability, and reliable communication across backend services.}
    \resumeItemListEnd

  \resumeProjectHeading
    {\textbf{Elixir Framework (Personal Project)} $|$ \emph{Open Source, Microservices}}{Ongoing}
    \resumeItemListStart
      \resumeItem{Developed a wrapper framework to simplify microservices development for CRUD operations in REST APIs, accelerating development cycles.}
    \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROFESSIONAL INTERESTS-----------
\section{Professional Interests}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
   Open to opportunities in: \textbf{Backend Engineering} $|$ \textbf{Full-Stack Development} $|$ \textbf{Technical Leadership} $|$ \textbf{Platform Engineering} $|$ \textbf{DevOps/SRE}
  }}
\end{itemize}
%-------------------------------------------
\end{document}